### 2008-03-06 trunk/SAiP/Module1/H3/doc/architecturaldescription.tex
Question 1 completed.

\fixme{Answer question 2.1}

@@

\subsubsection{Decomposition}

@@

@@

>>>>

@@

\subsubsection{Uses}

The \emph{uses structure} shows how elements are related with regard
to usage. One perspective of the uses structure is that the
elements in the figure are ''Overview创, ''Basket创 and ''Data创
which are all related and the database which is only related
to ''Data创. This shows that the overview page and the basket
has been decoupled from the database which therefore can be
replaced without affecting them.

\subsubsection{Layered}

Another perspective is that the users, the webserver and the
database are elements where the relations show that the users
use the webserver and the webserver uses the database. This
also shows the that the architecture is a
\emph{strictly layered structure} where the users cannot
access the database directly.

@@

As there are several users, the elements of the
\emph{strictly layered structure} can also be seen as a
\emph{client-server structure}, where the users are clients
and the webserver is a server. The webserver can also be
seen as a client to the database server. This would make it
possible to archieve better performance if several webservers
are used to make load balancing of the user requests.

@@

With regard to a \emph{deployment structure}, the figure shows
that the overview page, the basket and the domain model (elements)
are allocated to (relations) on the webserver and the database is
allocated to its own server.
